\chapter{Methodology}\label{ch4}

\section{Proposed Methodology}
In order to build a knowledge graph from tweets, we can divide our problem into these sub-problems. They are:
\begin{itemize}
\item Extracting information / tuples from tweets 
\item Merging those tuples with External Knowledge graphs
\item disambiguating after Merging 
\end{itemize} 
These two hypothesis are elaborated below: 

\Section{ Extracting Information or Tuples from tweets }
We know that tweets have very limited data. for example, 
\textit{ @ImRo45 is back in the Test squad for India’s tour of Australia. } is a tweet. Someone with adequate knowledge in cricket
may assume that this is about a game but otherwise, there is very little information in this tweet. 
Also, words like prepositions (of, in, for) , articles (a, the) have almost no value. On the contrary, `India', `tour', `Australia' 
are inpoetant words here. 
So, we have to extract these \textit{ important } words into \textit{ tuples } of the form $<u, e, v>$ . \\
 Define tuple of a graph $<u, e, v>$ where $ u $ is starting node, $ v $ is ending node and $ e $ is an edge between $ u $ and $v $. \\

this can be done in two ways: 
\begin{itemize}
\item Machine Learning 
\item JAPE 
\end{itemize} 
\\
In machine learning approach, one has to divide the dataset into `training dataset'  and `test dataset' . 
After that, one has to manually annotate the test dataset by marking possible tuples. After that, some machine learning algorithm
 can be trained on the test dataset and finally use it on the test dataset. 
\\ 
JAPE stands for `Jolly And Pleasant Experience'. It is a special kind of pattern matching language in GATE developer. 
By writting rules in JAPE , one can fine-tune GATE developer to extract necessary information which is in this case, 
finding the appropriate tuples. 
\\ 
In our methodology, we used JAPE. The reason is that, in previous works, other researchers  
~\cite{ref1DeepLearning} have already used machine learning approaches in this stage. Besides, we know 
that a machine learning algorithm is only as good as its training dataset. Using JAPE, detect tuples 
better.   


\section{ Merging Tuples with External Knowledge Graphs }
Since we have very limited data in our tweets, we need the help of an external knowledge graph to build 
up our version of knowledge graph. Suppose, in the previous step, we got this tuple: \testit{Alice loves Bob} here $<u, e, v> = <Alice, love, Bob>$.
Now the problem is that we need to identify who Alice and Bob really are, ie, if Alice is an actor , a fictional character or someone else.

For this can use Freebase, DBpedia etc as a source of external knowledge graph.
In our case, we took the liberty to use DBpedia. How to extract data from DBpedia is given below: 
\subsection{SPARQL}
One way to get data from DBpedia is to use the SPARQL. We can write queries in this language, such as 

In our case , we have nodes $ u $ and $ v $, so we can fetch datas that are related to both of them and make an intersection of those. 
But practically, this intersection returns a huge list of tentative tuples.  We can set a limit in our query to 
restrict our results' size. But still we need to disambiguate the results. For this, the next section comes into play.

\section{ disambiguating after Merging }
For each tuple <u,e,v> , we have a set of tentative tuples from dbpedia. We have to select only one of 
them. For this there are several ways:
\subsection{Relatedness}
 We can compute $ relatedness $ of two articles , $a$ , $b$ using the formula 
  $ relatedness(a,b) = \frac{\log(max(|A|, |B|)) - \log(A \cap B) }{ \log(W) - \log(max(|A|, |B|)) } $


\endinput